---
title: "Meta-Analysis of Placebo-Arm Change in Generalized Myasthenia Gravis Immunotherapy Trials"
author: "Felipe J. S. Jones"
output:
  html_document:
    toc: true
    toc_depth: 2
---

This R Markdown document reproduces the meta-analysis reported in Jones et al.

Open `mg-placebo-meta-analysis.Rproj` in RStudio before running, so the working directory is set to the repository root and `mg_placebo_clean_v5.csv` is found by relative path. Running all chunks writes result CSVs and PDF figures to the repository root.

# Packages

```{r setup, message = FALSE, warning = FALSE}
library(metafor)
library(dplyr)
library(ggplot2)
library(tibble)
library(ggrepel)
library(scales)
```

# Load and prepare data

```{r}
df <- read.csv("mg_placebo_clean_v5.csv", stringsAsFactors = FALSE) |>
  mutate(
    phase           = as.character(phase),
    route           = factor(route, levels = c("IV", "SC", "PO")),
    year            = as.integer(year),
    era_2017        = factor(ifelse(year >= 2017, "2017_plus", "pre_2017"),
                             levels = c("pre_2017", "2017_plus")),
    crossover       = study_id %in% c("Howard 2013", "Tindall 1993"),
    steroid_change  = factor(steroid_change, levels = c("Stable", "Taper")),
    rescue_rate_num = as.numeric(rescue_rate)
  )
```

# Analysis subsets

MG-ADL: excludes 5 studies not reporting MG-ADL  
QMG: excludes 3 studies with missing SD  
MGC: all studies with change and variance available

```{r}
d_mgadl <- df |> filter(!is.na(mgadl_change), !is.na(mgadl_vi))
d_qmg   <- df |> filter(!is.na(qmg_change),   !is.na(qmg_vi))
d_mgc   <- df |> filter(!is.na(mgc_change),   !is.na(mgc_vi))
```

# Helper functions

```{r}
run_primary <- function(data, yi_col, vi_col, label) {
  m <- rma(yi = data[[yi_col]], vi = data[[vi_col]],
           method = "REML", test = "knha",
           slab = data$study_id, data = data)
  cat("\n", strrep("=", 60), "\n", label, "\n", strrep("=", 60), "\n", sep = "")
  print(summary(m))
  pi <- predict(m, level = 0.95)
  cat(sprintf("\n95%% Prediction interval: [%.3f, %.3f]\n", pi$pi.lb, pi$pi.ub))
  cat("\ntau^2 profile CI:\n"); print(confint(m))
  m
}

run_metareg <- function(data, yi_col, vi_col, moderator_formula, label, mod_label) {
  m <- rma(yi = data[[yi_col]], vi = data[[vi_col]],
           mods = moderator_formula,
           method = "REML", test = "knha",
           slab = data$study_id, data = data)
  cat(sprintf("\n[%s | %s -- k=%d]\n", label, mod_label, m$k))
  print(summary(m))
  m
}

run_subgroup <- function(data, yi_col, vi_col, outcome_label, subset_label) {
  if (nrow(data) < 3) {
    cat(sprintf("  %-30s  k=%d -- too few studies\n", subset_label, nrow(data)))
    return(invisible(NULL))
  }
  m  <- rma(yi = data[[yi_col]], vi = data[[vi_col]],
            method = "REML", test = "knha",
            slab = data$study_id, data = data)
  pi <- predict(m)
  cat(sprintf("  %-30s  k=%2d  est=%6.3f [%6.3f, %6.3f]  PI [%6.3f, %6.3f]  I2=%.1f%%\n",
              subset_label, nrow(data),
              as.numeric(m$b), m$ci.lb, m$ci.ub, pi$pi.lb, pi$pi.ub, m$I2))
  m
}

results_table <- function(model, outcome_label, subgroup_label = NA_character_) {
  pi      <- predict(model)
  ci_tau2 <- confint(model)$random
  tibble(
    Subgroup      = subgroup_label,
    Outcome       = outcome_label,
    k             = model$k,
    Estimate      = round(model$b[1], 3),
    CI_lower      = round(model$ci.lb, 3),
    CI_upper      = round(model$ci.ub, 3),
    PI_lower      = round(pi$pi.lb, 3),
    PI_upper      = round(pi$pi.ub, 3),
    I2_pct        = round(model$I2, 1),
    tau2          = round(model$tau2, 4),
    tau2_CI_lower = round(ci_tau2["tau^2", "ci.lb"], 4),
    tau2_CI_upper = round(ci_tau2["tau^2", "ci.ub"], 4),
    Q_p           = round(model$QEp, 4)
  )
}

extract_mr <- function(model, moderator_label, outcome_label, n) {
  cs  <- coef(summary(model))
  row <- if (nrow(cs) > 1) cs[2, ] else cs[1, ]
  tibble(
    Outcome   = outcome_label,
    Moderator = moderator_label,
    k         = n,
    beta      = round(as.numeric(row[["estimate"]]), 4),
    SE        = round(as.numeric(row[["se"]]),       4),
    p_value   = round(as.numeric(row[["pval"]]),     4),
    R2        = round(max(0, model$R2), 1)
  )
}
```

# Primary pooled estimates

```{r}
m_mgadl <- run_primary(d_mgadl, "mgadl_change", "mgadl_vi", "MG-ADL")
m_qmg   <- run_primary(d_qmg,   "qmg_change",   "qmg_vi",   "QMG")
m_mgc   <- run_primary(d_mgc,   "mgc_change",   "mgc_vi",   "MGC")
```

# Forest plots

```{r}
plot_primary_forest <- function(model, data, label, filename, width = 10, height = NULL) {
  if (is.null(height)) height <- max(6, 0.3 * model$k + 3)
  ord <- order(data$year)
  pdf(filename, width = width, height = height)
  forest.rma(
    model, order = ord, slab = data$study_id,
    xlab    = paste0("Mean change from baseline (", label, ")"),
    main    = paste0("Placebo arm \u2212 ", label),
    header  = c("Study", "Mean change [95% CI]"),
    refline = 0, col = "steelblue",
    addfit = TRUE, addcred = TRUE, shade = "zebra"
  )
  text(x = par("usr")[1], y = -1.5,
       labels = bquote(I^2 == .(sprintf("%.1f%%", model$I2)) ~
                       "  " ~ tau^2 == .(sprintf("%.3f", model$tau2))),
       adj = 0, cex = 0.8)
  dev.off()
}

plot_primary_forest(m_mgadl, d_mgadl, "MG-ADL", "forest_mgadl_primary.pdf")
plot_primary_forest(m_qmg,   d_qmg,   "QMG",    "forest_qmg_primary.pdf")
plot_primary_forest(m_mgc,   d_mgc,   "MGC",    "forest_mgc_primary.pdf")
```

# Subgroup analyses

Subgroups: contemporary (2017+), stable steroid background therapy, phase 3 only, excluding crossover trials.

```{r}
# Subset definitions
d_mgadl_modern <- filter(d_mgadl, era_2017 == "2017_plus")
d_qmg_modern   <- filter(d_qmg,   era_2017 == "2017_plus")
d_mgc_modern   <- filter(d_mgc,   era_2017 == "2017_plus")

d_mgadl_stable <- filter(d_mgadl, steroid_change == "Stable")
d_qmg_stable   <- filter(d_qmg,   steroid_change == "Stable")
d_mgc_stable   <- filter(d_mgc,   steroid_change == "Stable")

d_mgadl_p3 <- filter(d_mgadl, phase == "3")
d_qmg_p3   <- filter(d_qmg,   phase == "3")
d_mgc_p3   <- filter(d_mgc,   phase == "3")

d_mgadl_nx <- filter(d_mgadl, !crossover)
d_qmg_nx   <- filter(d_qmg,   !crossover)
d_mgc_nx   <- filter(d_mgc,   !crossover)

# Fit pooled models for each subgroup
m_mgadl_modern <- run_subgroup(d_mgadl_modern, "mgadl_change", "mgadl_vi", "MG-ADL", "Contemporary (2017+)")
m_qmg_modern   <- run_subgroup(d_qmg_modern,   "qmg_change",   "qmg_vi",   "QMG",    "Contemporary (2017+)")
m_mgc_modern   <- run_subgroup(d_mgc_modern,   "mgc_change",   "mgc_vi",   "MGC",    "Contemporary (2017+)")

m_mgadl_stable <- run_subgroup(d_mgadl_stable, "mgadl_change", "mgadl_vi", "MG-ADL", "Stable steroids only")
m_qmg_stable   <- run_subgroup(d_qmg_stable,   "qmg_change",   "qmg_vi",   "QMG",    "Stable steroids only")
m_mgc_stable   <- run_subgroup(d_mgc_stable,   "mgc_change",   "mgc_vi",   "MGC",    "Stable steroids only")

m_mgadl_p3 <- run_subgroup(d_mgadl_p3, "mgadl_change", "mgadl_vi", "MG-ADL", "Phase 3 only")
m_qmg_p3   <- run_subgroup(d_qmg_p3,   "qmg_change",   "qmg_vi",   "QMG",    "Phase 3 only")
m_mgc_p3   <- run_subgroup(d_mgc_p3,   "mgc_change",   "mgc_vi",   "MGC",    "Phase 3 only")

m_mgadl_nx <- run_subgroup(d_mgadl_nx, "mgadl_change", "mgadl_vi", "MG-ADL", "Excluding crossover")
m_qmg_nx   <- run_subgroup(d_qmg_nx,   "qmg_change",   "qmg_vi",   "QMG",    "Excluding crossover")
m_mgc_nx   <- run_subgroup(d_mgc_nx,   "mgc_change",   "mgc_vi",   "MGC",    "Excluding crossover")
```

## Forest plots for each subgroup

```{r}
plot_subgroup_forest <- function(model, slabs, outcome_label, subset_label, filename,
                                 width = 10, height = NULL) {
  if (is.null(height)) height <- max(6, 0.3 * model$k + 3)
  pdf(filename, width = width, height = height)
  forest.rma(
    model, slab = slabs,
    xlab    = paste0("Mean change from baseline (", outcome_label, ")"),
    main    = paste0("Placebo arm \u2212 ", outcome_label, " (", subset_label, ")"),
    addcred = TRUE, refline = 0, col = "steelblue", shade = "zebra"
  )
  text(x = par("usr")[1], y = -1.5,
       labels = bquote(I^2 == .(sprintf("%.1f%%", model$I2)) ~
                       "  " ~ tau^2 == .(sprintf("%.3f", model$tau2))),
       adj = 0, cex = 0.8)
  dev.off()
}

# Contemporary (2017+)
plot_subgroup_forest(m_mgadl_modern, d_mgadl_modern$study_id, "MG-ADL", "2017+", "forest_mgadl_modern.pdf")
plot_subgroup_forest(m_qmg_modern,   d_qmg_modern$study_id,   "QMG",    "2017+", "forest_qmg_modern.pdf")
plot_subgroup_forest(m_mgc_modern,   d_mgc_modern$study_id,   "MGC",    "2017+", "forest_mgc_modern.pdf")

# Stable steroid background
plot_subgroup_forest(m_mgadl_stable, d_mgadl_stable$study_id, "MG-ADL", "stable background therapy", "forest_mgadl_stable.pdf")
plot_subgroup_forest(m_qmg_stable,   d_qmg_stable$study_id,   "QMG",    "stable background therapy", "forest_qmg_stable.pdf")
plot_subgroup_forest(m_mgc_stable,   d_mgc_stable$study_id,   "MGC",    "stable background therapy", "forest_mgc_stable.pdf")

# Phase 3 only
plot_subgroup_forest(m_mgadl_p3, d_mgadl_p3$study_id, "MG-ADL", "Phase 3 only", "forest_mgadl_phase3.pdf")
plot_subgroup_forest(m_qmg_p3,   d_qmg_p3$study_id,   "QMG",    "Phase 3 only", "forest_qmg_phase3.pdf")
plot_subgroup_forest(m_mgc_p3,   d_mgc_p3$study_id,   "MGC",    "Phase 3 only", "forest_mgc_phase3.pdf")

# Excluding crossover trials
plot_subgroup_forest(m_mgadl_nx, d_mgadl_nx$study_id, "MG-ADL", "excluding crossover", "forest_mgadl_nocrossover.pdf")
plot_subgroup_forest(m_qmg_nx,   d_qmg_nx$study_id,   "QMG",    "excluding crossover", "forest_qmg_nocrossover.pdf")
plot_subgroup_forest(m_mgc_nx,   d_mgc_nx$study_id,   "MGC",    "excluding crossover", "forest_mgc_nocrossover.pdf")
```

## Leave-one-out sensitivity

```{r}
loo_mgadl <- leave1out(m_mgadl, method = "REML")
loo_qmg   <- leave1out(m_qmg,   method = "REML")
loo_mgc   <- leave1out(m_mgc,   method = "REML")

plot_loo <- function(loo_obj, data, label, overall_model, filename, width = 9, height = 9) {
  pdf(filename, width = width, height = height)
  forest(x       = loo_obj$estimate,
         ci.lb   = loo_obj$ci.lb,
         ci.ub   = loo_obj$ci.ub,
         slab    = data$study_id,
         xlab    = paste0("Pooled ", label, " change (leave-one-out)"),
         main    = paste0("Leave-one-out sensitivity \u2212 ", label),
         refline = as.numeric(overall_model$b),
         col     = "steelblue", shade = "zebra")
  dev.off()
}

plot_loo(loo_mgadl, d_mgadl, "MG-ADL", m_mgadl, "loo_mgadl.pdf", 9, 9)
plot_loo(loo_qmg,   d_qmg,   "QMG",    m_qmg,   "loo_qmg.pdf",   9, 10)
plot_loo(loo_mgc,   d_mgc,   "MGC",    m_mgc,   "loo_mgc.pdf",   9, 8)
```

# Meta-regression: study-level predictors

Pre-specified moderators (univariable):  
1. Mean age, 
2. Female %, 
3. MGFA % class III-V, 
4. AChR-seropositive %,  
5. Route (ref = IV), 
6. Phase (ref = 2),  
7. Assessment timepoint (weeks),  
8. Trial era (2017+ vs pre-2017),  
9. Steroid change (Taper vs Stable),  
10. Placebo-arm rescue therapy rate (%).

```{r}
# MG-ADL
mr_mgadl_age    <- run_metareg(filter(d_mgadl, !is.na(age_mean)),
                               "mgadl_change","mgadl_vi", ~age_mean,         "MG-ADL","Mean age")
mr_mgadl_sex    <- run_metareg(filter(d_mgadl, !is.na(female_pct)),
                               "mgadl_change","mgadl_vi", ~female_pct,       "MG-ADL","Female%")
mr_mgadl_mgfa   <- run_metareg(filter(d_mgadl, !is.na(mgfa_severe_pct)),
                               "mgadl_change","mgadl_vi", ~mgfa_severe_pct,  "MG-ADL","MGFA %III-V")
mr_mgadl_achr   <- run_metareg(filter(d_mgadl, !is.na(achr_pct)),
                               "mgadl_change","mgadl_vi", ~achr_pct,         "MG-ADL","AChR%")
mr_mgadl_route  <- run_metareg(d_mgadl,
                               "mgadl_change","mgadl_vi", ~route,            "MG-ADL","Route (ref=IV)")
mr_mgadl_phase  <- run_metareg(d_mgadl,
                               "mgadl_change","mgadl_vi", ~phase,            "MG-ADL","Phase (ref=2)")
mr_mgadl_tp     <- run_metareg(filter(d_mgadl, !is.na(tp_mgadl_wk)),
                               "mgadl_change","mgadl_vi", ~tp_mgadl_wk,      "MG-ADL","Timepoint (wk)")
mr_mgadl_era17  <- run_metareg(d_mgadl,
                               "mgadl_change","mgadl_vi", ~era_2017,         "MG-ADL","Era 2017+ vs pre")
mr_mgadl_taper  <- run_metareg(d_mgadl,
                               "mgadl_change","mgadl_vi", ~steroid_change,   "MG-ADL","Steroid (Taper vs Stable)")
mr_mgadl_rescue <- run_metareg(filter(d_mgadl, !is.na(rescue_rate_num)),
                               "mgadl_change","mgadl_vi", ~rescue_rate_num,  "MG-ADL","Rescue rate (%)")

# QMG
mr_qmg_age    <- run_metareg(filter(d_qmg, !is.na(age_mean)),
                             "qmg_change","qmg_vi", ~age_mean,         "QMG","Mean age")
mr_qmg_sex    <- run_metareg(filter(d_qmg, !is.na(female_pct)),
                             "qmg_change","qmg_vi", ~female_pct,       "QMG","Female%")
mr_qmg_mgfa   <- run_metareg(filter(d_qmg, !is.na(mgfa_severe_pct)),
                             "qmg_change","qmg_vi", ~mgfa_severe_pct,  "QMG","MGFA %III-V")
mr_qmg_achr   <- run_metareg(filter(d_qmg, !is.na(achr_pct)),
                             "qmg_change","qmg_vi", ~achr_pct,         "QMG","AChR%")
mr_qmg_route  <- run_metareg(d_qmg,
                             "qmg_change","qmg_vi", ~route,            "QMG","Route (ref=IV)")
mr_qmg_phase  <- run_metareg(d_qmg,
                             "qmg_change","qmg_vi", ~phase,            "QMG","Phase (ref=2)")
mr_qmg_tp     <- run_metareg(filter(d_qmg, !is.na(tp_qmg_wk)),
                             "qmg_change","qmg_vi", ~tp_qmg_wk,        "QMG","Timepoint (wk)")
mr_qmg_era17  <- run_metareg(d_qmg,
                             "qmg_change","qmg_vi", ~era_2017,         "QMG","Era 2017+ vs pre")
mr_qmg_taper  <- run_metareg(d_qmg,
                             "qmg_change","qmg_vi", ~steroid_change,   "QMG","Steroid (Taper vs Stable)")
mr_qmg_rescue <- run_metareg(filter(d_qmg, !is.na(rescue_rate_num)),
                             "qmg_change","qmg_vi", ~rescue_rate_num,  "QMG","Rescue rate (%)")

# MGC
mr_mgc_age    <- run_metareg(filter(d_mgc, !is.na(age_mean)),
                             "mgc_change","mgc_vi", ~age_mean,         "MGC","Mean age")
mr_mgc_sex    <- run_metareg(filter(d_mgc, !is.na(female_pct)),
                             "mgc_change","mgc_vi", ~female_pct,       "MGC","Female%")
mr_mgc_mgfa   <- run_metareg(filter(d_mgc, !is.na(mgfa_severe_pct)),
                             "mgc_change","mgc_vi", ~mgfa_severe_pct,  "MGC","MGFA %III-V")
mr_mgc_achr   <- run_metareg(filter(d_mgc, !is.na(achr_pct)),
                             "mgc_change","mgc_vi", ~achr_pct,         "MGC","AChR%")
mr_mgc_route  <- run_metareg(d_mgc,
                             "mgc_change","mgc_vi", ~route,            "MGC","Route (ref=IV)")
mr_mgc_phase  <- run_metareg(d_mgc,
                             "mgc_change","mgc_vi", ~phase,            "MGC","Phase (ref=2)")
mr_mgc_tp     <- run_metareg(filter(d_mgc, !is.na(tp_mgc_wk)),
                             "mgc_change","mgc_vi", ~tp_mgc_wk,        "MGC","Timepoint (wk)")
mr_mgc_era17  <- run_metareg(d_mgc,
                             "mgc_change","mgc_vi", ~era_2017,         "MGC","Era 2017+ vs pre")
mr_mgc_taper  <- run_metareg(d_mgc,
                             "mgc_change","mgc_vi", ~steroid_change,   "MGC","Steroid (Taper vs Stable)")
mr_mgc_rescue <- run_metareg(filter(d_mgc, !is.na(rescue_rate_num)),
                             "mgc_change","mgc_vi", ~rescue_rate_num,  "MGC","Rescue rate (%)")
```

# MCID probabilities

P(future trial mean change >= MCID) from the predictive distribution: t_{k-2} centered at mu, scale = sqrt(tau^2 + SE_mu^2).  
MCID thresholds: MG-ADL >= 2; QMG >= 2 or >=3; MGC >= 3.

```{r}
mcid_prob <- function(model, mcid, outcome_label, subgroup_label) {
  mu         <- as.numeric(model$beta)
  tau2       <- model$tau2
  se_mu      <- model$se
  k          <- model$k
  pred_scale <- sqrt(tau2 + se_mu^2)
  df_pred    <- max(k - 2L, 1L)

  # P(future trial mean <= -MCID) = P(improvement >= MCID)
  p_pred <- pt((-mcid - mu) / pred_scale, df = df_pred)
  # P(pooled mean <= -MCID)
  p_mean <- pt((-mcid - mu) / se_mu, df = k - 1L)

  tibble(
    Outcome        = outcome_label,
    Subgroup       = subgroup_label,
    MCID           = mcid,
    k              = k,
    mu             = round(mu,    3),
    tau2           = round(tau2,  4),
    SE_pooled      = round(se_mu, 3),
    Pred_scale     = round(pred_scale, 3),
    P_future_trial = round(p_pred * 100, 1),
    P_pooled_mean  = round(p_mean * 100, 1)
  )
}

results_mcid <- bind_rows(
  mcid_prob(m_mgadl,        2, "MG-ADL", "All studies"),
  mcid_prob(m_qmg,          2, "QMG",    "All studies (MCID=2)"),
  mcid_prob(m_qmg,          3, "QMG",    "All studies (MCID=3)"),
  mcid_prob(m_mgc,          3, "MGC",    "All studies"),
  mcid_prob(m_mgadl_modern, 2, "MG-ADL", "2017+"),
  mcid_prob(m_qmg_modern,   2, "QMG",    "2017+ (MCID=2)"),
  mcid_prob(m_qmg_modern,   3, "QMG",    "2017+ (MCID=3)"),
  mcid_prob(m_mgc_modern,   3, "MGC",    "2017+"),
  mcid_prob(m_mgadl_stable, 2, "MG-ADL", "Stable steroids only"),
  mcid_prob(m_qmg_stable,   3, "QMG",    "Stable steroids only"),
  mcid_prob(m_mgc_stable,   3, "MGC",    "Stable steroids only")
)
print(results_mcid, row.names = FALSE)
write.csv(results_mcid, "results_mcid.csv", row.names = FALSE)

# Contemporary-only MCID (for Table 4B)
results_mcid_modern <- bind_rows(
  mcid_prob(m_mgadl_modern, 2, "MG-ADL", "2017+ contemporary"),
  mcid_prob(m_qmg_modern,   2, "QMG",    "2017+ contemporary (MCID=2)"),
  mcid_prob(m_qmg_modern,   3, "QMG",    "2017+ contemporary (MCID=3)"),
  mcid_prob(m_mgc_modern,   3, "MGC",    "2017+ contemporary")
)
write.csv(results_mcid_modern, "results_mcid_contemporary.csv", row.names = FALSE)
```

# Within-trial SD of placebo-arm change (descriptive)

```{r}
within_sd <- bind_rows(
  tibble(Outcome = "MG-ADL", Subset = "All trials",
         k = sum(!is.na(d_mgadl$mgadl_change_sd)),
         Median = round(median(d_mgadl$mgadl_change_sd, na.rm = TRUE), 2),
         IQR_lower = round(quantile(d_mgadl$mgadl_change_sd, 0.25, na.rm = TRUE), 2),
         IQR_upper = round(quantile(d_mgadl$mgadl_change_sd, 0.75, na.rm = TRUE), 2)),
  tibble(Outcome = "QMG", Subset = "All trials",
         k = sum(!is.na(d_qmg$qmg_change_sd)),
         Median = round(median(d_qmg$qmg_change_sd, na.rm = TRUE), 2),
         IQR_lower = round(quantile(d_qmg$qmg_change_sd, 0.25, na.rm = TRUE), 2),
         IQR_upper = round(quantile(d_qmg$qmg_change_sd, 0.75, na.rm = TRUE), 2)),
  tibble(Outcome = "MGC", Subset = "All trials",
         k = sum(!is.na(d_mgc$mgc_change_sd)),
         Median = round(median(d_mgc$mgc_change_sd, na.rm = TRUE), 2),
         IQR_lower = round(quantile(d_mgc$mgc_change_sd, 0.25, na.rm = TRUE), 2),
         IQR_upper = round(quantile(d_mgc$mgc_change_sd, 0.75, na.rm = TRUE), 2)),
  tibble(Outcome = "MG-ADL", Subset = "Contemporary (2017+)",
         k = sum(!is.na(d_mgadl_modern$mgadl_change_sd)),
         Median = round(median(d_mgadl_modern$mgadl_change_sd, na.rm = TRUE), 2),
         IQR_lower = round(quantile(d_mgadl_modern$mgadl_change_sd, 0.25, na.rm = TRUE), 2),
         IQR_upper = round(quantile(d_mgadl_modern$mgadl_change_sd, 0.75, na.rm = TRUE), 2)),
  tibble(Outcome = "QMG", Subset = "Contemporary (2017+)",
         k = sum(!is.na(d_qmg_modern$qmg_change_sd)),
         Median = round(median(d_qmg_modern$qmg_change_sd, na.rm = TRUE), 2),
         IQR_lower = round(quantile(d_qmg_modern$qmg_change_sd, 0.25, na.rm = TRUE), 2),
         IQR_upper = round(quantile(d_qmg_modern$qmg_change_sd, 0.75, na.rm = TRUE), 2)),
  tibble(Outcome = "MGC", Subset = "Contemporary (2017+)",
         k = sum(!is.na(d_mgc_modern$mgc_change_sd)),
         Median = round(median(d_mgc_modern$mgc_change_sd, na.rm = TRUE), 2),
         IQR_lower = round(quantile(d_mgc_modern$mgc_change_sd, 0.25, na.rm = TRUE), 2),
         IQR_upper = round(quantile(d_mgc_modern$mgc_change_sd, 0.75, na.rm = TRUE), 2))
)
print(within_sd, row.names = FALSE)
write.csv(within_sd, "results_within_trial_sd.csv", row.names = FALSE)
```

# Summary tables

```{r}
# Primary results
res_tbl <- bind_rows(
  results_table(m_mgadl, "MG-ADL"),
  results_table(m_qmg,   "QMG"),
  results_table(m_mgc,   "MGC")
)
write.csv(res_tbl, "results_primary_summary.csv", row.names = FALSE)

# Subgroup table (15 rows: 5 subgroups x 3 outcomes)
subgroup_tbl <- bind_rows(
  results_table(m_mgadl,        "MG-ADL", "Primary (all trials)"),
  results_table(m_qmg,          "QMG",    "Primary (all trials)"),
  results_table(m_mgc,          "MGC",    "Primary (all trials)"),
  results_table(m_mgadl_modern, "MG-ADL", "Contemporary (2017+)"),
  results_table(m_qmg_modern,   "QMG",    "Contemporary (2017+)"),
  results_table(m_mgc_modern,   "MGC",    "Contemporary (2017+)"),
  results_table(m_mgadl_stable, "MG-ADL", "Stable steroids only"),
  results_table(m_qmg_stable,   "QMG",    "Stable steroids only"),
  results_table(m_mgc_stable,   "MGC",    "Stable steroids only"),
  results_table(m_mgadl_p3,     "MG-ADL", "Phase 3 only"),
  results_table(m_qmg_p3,       "QMG",    "Phase 3 only"),
  results_table(m_mgc_p3,       "MGC",    "Phase 3 only"),
  results_table(m_mgadl_nx,     "MG-ADL", "Excluding crossover"),
  results_table(m_qmg_nx,       "QMG",    "Excluding crossover"),
  results_table(m_mgc_nx,       "MGC",    "Excluding crossover")
)
write.csv(subgroup_tbl, "results_subgroup_summary.csv", row.names = FALSE)

# Meta-regression table (Table 3 source)
mr_summary <- bind_rows(
  # MG-ADL
  extract_mr(mr_mgadl_age,    "Mean age",                       "MG-ADL", sum(!is.na(d_mgadl$age_mean))),
  extract_mr(mr_mgadl_sex,    "Female%",                        "MG-ADL", sum(!is.na(d_mgadl$female_pct))),
  extract_mr(mr_mgadl_mgfa,   "MGFA %III-V",                    "MG-ADL", sum(!is.na(d_mgadl$mgfa_severe_pct))),
  extract_mr(mr_mgadl_achr,   "AChR%",                          "MG-ADL", sum(!is.na(d_mgadl$achr_pct))),
  extract_mr(mr_mgadl_route,  "Route (ref=IV)",                 "MG-ADL", nrow(d_mgadl)),
  extract_mr(mr_mgadl_phase,  "Phase (ref=2)",                  "MG-ADL", nrow(d_mgadl)),
  extract_mr(mr_mgadl_tp,     "Timepoint (wk)",                 "MG-ADL", sum(!is.na(d_mgadl$tp_mgadl_wk))),
  extract_mr(mr_mgadl_era17,  "Era (2017+ vs pre-2017)",        "MG-ADL", nrow(d_mgadl)),
  extract_mr(mr_mgadl_taper,  "Steroid (Taper vs Stable)",      "MG-ADL", nrow(d_mgadl)),
  extract_mr(mr_mgadl_rescue, "Rescue rate (%)",                "MG-ADL", sum(!is.na(d_mgadl$rescue_rate_num))),
  # QMG
  extract_mr(mr_qmg_age,    "Mean age",                  "QMG", sum(!is.na(d_qmg$age_mean))),
  extract_mr(mr_qmg_sex,    "Female%",                   "QMG", sum(!is.na(d_qmg$female_pct))),
  extract_mr(mr_qmg_mgfa,   "MGFA %III-V",               "QMG", sum(!is.na(d_qmg$mgfa_severe_pct))),
  extract_mr(mr_qmg_achr,   "AChR%",                     "QMG", sum(!is.na(d_qmg$achr_pct))),
  extract_mr(mr_qmg_route,  "Route (ref=IV)",            "QMG", nrow(d_qmg)),
  extract_mr(mr_qmg_phase,  "Phase (ref=2)",             "QMG", nrow(d_qmg)),
  extract_mr(mr_qmg_tp,     "Timepoint (wk)",            "QMG", sum(!is.na(d_qmg$tp_qmg_wk))),
  extract_mr(mr_qmg_era17,  "Era (2017+ vs pre-2017)",   "QMG", nrow(d_qmg)),
  extract_mr(mr_qmg_taper,  "Steroid (Taper vs Stable)", "QMG", nrow(d_qmg)),
  extract_mr(mr_qmg_rescue, "Rescue rate (%)",           "QMG", sum(!is.na(d_qmg$rescue_rate_num))),
  # MGC
  extract_mr(mr_mgc_age,    "Mean age",                  "MGC", sum(!is.na(d_mgc$age_mean))),
  extract_mr(mr_mgc_sex,    "Female%",                   "MGC", sum(!is.na(d_mgc$female_pct))),
  extract_mr(mr_mgc_mgfa,   "MGFA %III-V",               "MGC", sum(!is.na(d_mgc$mgfa_severe_pct))),
  extract_mr(mr_mgc_achr,   "AChR%",                     "MGC", sum(!is.na(d_mgc$achr_pct))),
  extract_mr(mr_mgc_route,  "Route (ref=IV)",            "MGC", nrow(d_mgc)),
  extract_mr(mr_mgc_phase,  "Phase (ref=2)",             "MGC", nrow(d_mgc)),
  extract_mr(mr_mgc_tp,     "Timepoint (wk)",            "MGC", sum(!is.na(d_mgc$tp_mgc_wk))),
  extract_mr(mr_mgc_era17,  "Era (2017+ vs pre-2017)",   "MGC", nrow(d_mgc)),
  extract_mr(mr_mgc_taper,  "Steroid (Taper vs Stable)", "MGC", nrow(d_mgc)),
  extract_mr(mr_mgc_rescue, "Rescue rate (%)",           "MGC", sum(!is.na(d_mgc$rescue_rate_num)))
)
write.csv(mr_summary, "results_metaregression.csv", row.names = FALSE)
```
