---
title: "Placebo-Arm Change in Generalized Myasthenia Gravis Immunotherapy Trials: A Meta-analysis"
author: "Felipe J. S. Jones"
output:
  html_document:
    toc: true
    toc_depth: 2
---

This R Markdown document reproduces the meta-analysis reported in the manuscript.

Open `mg-placebo-meta-analysis.Rproj` in RStudio before running, so the working directory is set to the repository root and `mg_placebo_clean_v5.csv` is found by relative path.

# Packages

```{r setup, message = FALSE, warning = FALSE}
library(metafor)
library(dplyr)
library(ggplot2)
library(tibble)
library(ggrepel)
library(scales)
library(here)
```

# Load and prepare data

```{r}
df <- read.csv("mg_placebo_clean_v5.csv", stringsAsFactors = FALSE) |>
  mutate(
    phase     = factor(phase, levels = c("2","3"), labels = c("Phase 2","Phase 3")),
    route           = factor(route, levels = c("IV", "SC", "PO")),
    year            = as.integer(year),
    era_2017        = factor(ifelse(year >= 2017, "2017_plus", "pre_2017"),
                             levels = c("pre_2017", "2017_plus")),
    crossover = factor(ifelse(study_id %in% c("Howard 2013","Tindall 1993"),
                          "Crossover","Parallel"),
                   levels = c("Parallel","Crossover")),
    steroid_change  = factor(steroid_change, levels = c("Stable", "Taper")),
    rescue_rate_num = as.numeric(rescue_rate)
  )
```

## Risk of bias (Cochrane RoB 1, seven domains)

```{r}
rob_raw <- read.csv(
  "review-640239-consensus-only-quality-assessment-study-per-row-20260508015146.csv",
  header = FALSE, stringsAsFactors = FALSE, skip = 2
)

jcols <- c(2, 5, 8, 11, 14, 17, 20)
rob <- data.frame(study_id = trimws(rob_raw[[1]]), rob_raw[jcols],
                  stringsAsFactors = FALSE)
names(rob)[-1] <- c("d1","d2","d3","d4","d5","d6","d7")
rob <- rob[rob$study_id != "", ]

# Per-domain symbols (A-G): + low, ? unclear, - high
sym_map <- c(low = "+", unclear = "?", high = "\u2212")
to_sym  <- function(x) sym_map[tolower(trimws(x))]
rob[paste0("rob_", LETTERS[1:7])] <- lapply(rob[paste0("d", 1:7)], to_sym)

# Overall RoB = worst domain
sev <- c(low = 1, unclear = 2, high = 3)
rob$rob_overall <- vapply(seq_len(nrow(rob)), function(i) {
  vals <- tolower(trimws(unlist(rob[i, paste0("d", 1:7)])))
  names(which.max(sev[vals]))
}, character(1))
rob$rob_overall <- factor(rob$rob_overall, levels = c("low","unclear","high"),
                          labels = c("Low","Some concerns","High"))

df <- left_join(df,
                rob[, c("study_id", "rob_overall", paste0("rob_", LETTERS[1:7]))],
                by = "study_id")
stopifnot(all(!is.na(df$rob_overall)))
```

# Analysis subsets

```{r}
d_mgadl <- df |> filter(!is.na(mgadl_change), !is.na(mgadl_vi))
d_qmg   <- df |> filter(!is.na(qmg_change),   !is.na(qmg_vi))
d_mgc   <- df |> filter(!is.na(mgc_change),   !is.na(mgc_vi))
```

# Helper functions

```{r}
run_primary <- function(data, yi_col, vi_col, label) {
  m <- rma(yi = data[[yi_col]], vi = data[[vi_col]],
           method = "REML", test = "knha", slab = data$study_id, data = data)
  cat("\n", strrep("=", 60), "\n", label, "\n", strrep("=", 60), "\n", sep = "")
  print(summary(m))
  pi <- predict(m, level = 0.95)
  cat(sprintf("\n95%% Prediction interval: [%.3f, %.3f]\n", pi$pi.lb, pi$pi.ub))
  cat("\ntau^2 profile CI:\n"); print(confint(m))
  m
}

run_metareg <- function(data, yi_col, vi_col, moderator_formula, label, mod_label) {
  m <- rma(yi = data[[yi_col]], vi = data[[vi_col]], mods = moderator_formula,
           method = "REML", test = "knha", slab = data$study_id, data = data)
  cat(sprintf("\n[%s | %s -- k=%d]\n", label, mod_label, m$k))
  print(summary(m))
  m
}

run_subgroup <- function(data, yi_col, vi_col, outcome_label, subset_label) {
  if (nrow(data) < 3) {
    cat(sprintf("  %-30s  k=%d -- too few studies\n", subset_label, nrow(data)))
    return(invisible(NULL))
  }
  m  <- rma(yi = data[[yi_col]], vi = data[[vi_col]],
            method = "REML", test = "knha", slab = data$study_id, data = data)
  pi <- predict(m)
  cat(sprintf("  %-30s  k=%2d  est=%6.3f [%6.3f, %6.3f]  PI [%6.3f, %6.3f]  I2=%.1f%%\n",
              subset_label, nrow(data),
              as.numeric(m$b), m$ci.lb, m$ci.ub, pi$pi.lb, pi$pi.ub, m$I2))
  m
}

results_table <- function(model, outcome_label, subgroup_label = NA_character_) {
  pi      <- predict(model)
  ci_tau2 <- confint(model)$random
  tibble(
    Subgroup = subgroup_label, Outcome = outcome_label, k = model$k,
    Estimate = round(model$b[1], 3),
    CI_lower = round(model$ci.lb, 3), CI_upper = round(model$ci.ub, 3),
    PI_lower = round(pi$pi.lb, 3),    PI_upper = round(pi$pi.ub, 3),
    I2_pct = round(model$I2, 1), tau2 = round(model$tau2, 4),
    tau2_CI_lower = round(ci_tau2["tau^2", "ci.lb"], 4),
    tau2_CI_upper = round(ci_tau2["tau^2", "ci.ub"], 4),
    Q_p = round(model$QEp, 4)
  )
}

extract_mr <- function(model, moderator_label, outcome_label, n) {
  cs  <- coef(summary(model))
  row <- if (nrow(cs) > 1) cs[2, ] else cs[1, ]
  tibble(
    Outcome = outcome_label, Moderator = moderator_label, k = n,
    beta = round(as.numeric(row[["estimate"]]), 4),
    SE   = round(as.numeric(row[["se"]]),       4),
    p_value = round(as.numeric(row[["pval"]]),  4),
    R2   = round(max(0, model$R2), 1)
  )
}
```

# Grouped forest plot 

```{r}
fmtp <- function(p) if (p < 0.001) "< 0.001" else sprintf("= %.3f", p)

plot_forest_metafor_grouped <- function(data, yi_col, vi_col, change_col, sd_col,
                                        subgroup_col, subgroup_levels, subgroup_labels,
                                        outcome_label, filename,
                                        width = 19, height = NULL,
                                        axis_by = 1,
                                        gap_between = 3,
                                        font_scale = 1.65) {   # multiply all text sizes

  d <- data[!is.na(data[[subgroup_col]]), ]
  d[[subgroup_col]] <- factor(d[[subgroup_col]], levels = subgroup_levels)
  d <- d[order(d[[subgroup_col]], d$year), ]

  m_all <- rma(yi = d[[yi_col]], vi = d[[vi_col]], method = "REML", test = "knha",
               slab = d$study_id, data = d)
  m_mod <- rma(yi = d[[yi_col]], vi = d[[vi_col]],
               mods = as.formula(paste0("~ ", subgroup_col)),
               method = "REML", test = "knha", data = d)
  p_between <- m_mod$QMp

  grp_idx  <- split(seq_len(nrow(d)), d[[subgroup_col]])[subgroup_levels]
  grp_fits <- lapply(grp_idx, function(ix)
    rma(yi = d[[yi_col]][ix], vi = d[[vi_col]][ix], method = "REML", test = "knha"))

  ng    <- length(grp_idx)
  sizes <- vapply(grp_idx, length, integer(1))
  rows    <- numeric(0); headers <- numeric(ng); subtot <- numeric(ng)
  cur <- sum(sizes) + ng * 2 + (ng - 1) * gap_between + 2
  for (g in seq_len(ng)) {
    headers[g] <- cur + 1
    grp_rows   <- seq(cur, cur - sizes[g] + 1)
    rows       <- c(rows, grp_rows)
    subtot[g]  <- min(grp_rows) - 1.2
    extra      <- if (g == ng) 2.5 else 1.0   # room for PI bar + shifted annotation lines
    cur        <- subtot[g] - 2.0 - extra - gap_between
  }
  d <- d[unlist(grp_idx), ]
  rob_cols <- paste0("rob_", LETTERS[1:7])
  circ_col <- c("+"="#2c9c2c", "?"="#e8c020", "\u2212"="#cc2222")

  if (is.null(height)) height <- 0.28 * (nrow(d) + ng * gap_between) + 7

  ci      <- 1.96 * sqrt(d[[vi_col]])
  alim_lo <- floor(min(d[[yi_col]] - ci, na.rm = TRUE)) - 1   # widen plot left
  alim_hi <- ceiling(max(max(d[[yi_col]] + ci, na.rm = TRUE), 0)) + 1  # widen plot right
  aspan   <- alim_hi - alim_lo

  ## ---- Gutters sized to give the forest data region more of the width ----
  xlim_left  <- alim_lo - 4.2 * aspan     # left gutter (N, weight, RoB)
  xlim_right <- alim_hi + 3.4 * aspan     # right gutter holds 3 tight columns

  ## LEFT columns live in the left gutter
  x_n     <- alim_lo - 2.35 * aspan
  x_wt    <- alim_lo - 1.95 * aspan
  x_rob0  <- alim_lo - 1.60 * aspan
  x_rob_step <- 0.145 * aspan

  ## RIGHT columns: packed tight near the right edge
  x_ci    <- alim_hi + 1.30 * aspan       # Change [95% CI] (widest text)
  x_pi    <- alim_hi + 2.35 * aspan       # 95% PI
  x_sd    <- alim_hi + 3.00 * aspan       # SD

  est_ci <- sprintf("%.2f [%.2f, %.2f]", d[[yi_col]], d[[yi_col]] - ci, d[[yi_col]] + ci)
  wt_all <- weights(m_all)

  ## Overall block sits below the final subgroup's lowest annotation
  ## (final subgroup: het at subtot-2.0, between-group test at subtot-3.0)
  y_overall <- subtot[ng] - 5.0
  y_opi     <- y_overall - 1.0   # overall 95% PI bar, one row below diamond
  y_ohet    <- y_overall - 1.8

  render <- function() {
    par(mar = c(11, 4, 3, 2))

  metafor::forest(
    m_all,
    rows      = rows,
    ylim      = c(y_ohet - 0.8, max(headers) + 3),
    xlim      = c(xlim_left, xlim_right),
    alim      = c(alim_lo, alim_hi),
    at        = seq(alim_lo, alim_hi, by = axis_by),
    slab      = d$study_id,
    ilab      = cbind(d$n_placebo, sprintf("%.1f%%", wt_all),
                      est_ci, sprintf("%.1f", d[[sd_col]])),
    ilab.xpos = c(x_n, x_wt, x_ci, x_sd),
    header    = "Study",
    xlab      = paste0(outcome_label, " change from baseline"),
    refline   = 0, col = "steelblue", cex = 0.75 * font_scale,
    annotate  = FALSE, addfit = FALSE
  )

  op <- par(font = 2, cex = 0.72 * font_scale)
  text(x_n,  max(headers) + 2, "N")
  text(x_wt, max(headers) + 2, "Weight")
  text(x_rob0 + (0:6) * x_rob_step, max(headers) + 2, LETTERS[1:7])
  text(x_ci, max(headers) + 2, paste0(outcome_label, " [95% CI]"))
  text(x_pi, max(headers) + 2, "95% PI")  # PI reported only for pooled/subtotal rows (bars below diamonds)
  text(x_sd, max(headers) + 2, "SD")
  par(op)

  for (j in 1:7) {
    sym <- as.character(d[[rob_cols[j]]]); xj <- x_rob0 + (j - 1) * x_rob_step
    points(rep(xj, nrow(d)), rows, pch = 21, bg = circ_col[sym], col = "grey40", cex = 1.4 * font_scale)
    text(rep(xj, nrow(d)), rows, sym, cex = 0.55 * font_scale)
  }

  for (g in seq_len(ng)) {
    text(xlim_left, headers[g], subgroup_labels[g], pos = 4, font = 2, cex = 0.8 * font_scale)
    fit <- grp_fits[[g]]; pig <- predict(fit)
    addpoly(fit, row = subtot[g], mlab = "", col = "navy", cex = 0.75 * font_scale)
    ## 95% PI as a separate horizontal bar one row below the diamond
    segments(pig$pi.lb, subtot[g] - 1, pig$pi.ub, subtot[g] - 1, col = "navy", lwd = 1.4)
    segments(c(pig$pi.lb, pig$pi.ub), subtot[g] - 1 - 0.15,
             c(pig$pi.lb, pig$pi.ub), subtot[g] - 1 + 0.15, col = "navy", lwd = 1.4)
    text(x_ci, subtot[g], sprintf("%.2f [%.2f, %.2f]",
         as.numeric(fit$b), fit$ci.lb, fit$ci.ub), cex = 0.70 * font_scale, font = 2)
    text(x_pi, subtot[g] - 1, sprintf("[%.2f, %.2f]", pig$pi.lb, pig$pi.ub), cex = 0.70 * font_scale, font = 2)
    text(xlim_left, subtot[g] - 2.0, pos = 4, cex = 0.72 * font_scale,
         bquote(paste("Subgroup heterogeneity: ", I^2, "=", .(sprintf("%.1f%%", fit$I2)),
                      ", ", tau^2, "=", .(sprintf("%.3f", fit$tau2)),
                      ", p ", .(fmtp(fit$QEp)))))
    if (g == ng) {
      text(xlim_left, subtot[g] - 3.0, pos = 4, cex = 0.72 * font_scale,
           bquote(paste("Test for subgroup differences (HK): p ", .(fmtp(p_between)))))
    }
  }

  pi_all <- predict(m_all)
  addpoly(m_all, row = y_overall, mlab = "Overall (HK)", col = "black", cex = 0.8 * font_scale)
  ## 95% PI as a separate horizontal bar one row below the overall diamond
  segments(pi_all$pi.lb, y_opi, pi_all$pi.ub, y_opi, col = "black", lwd = 1.4)
  segments(c(pi_all$pi.lb, pi_all$pi.ub), y_opi - 0.15,
           c(pi_all$pi.lb, pi_all$pi.ub), y_opi + 0.15, col = "black", lwd = 1.4)
  text(xlim_left, y_opi, "95% prediction interval", pos = 4, cex = 0.70 * font_scale, font = 3)
  text(x_ci, y_overall, sprintf("%.2f [%.2f, %.2f]",
       as.numeric(m_all$b), m_all$ci.lb, m_all$ci.ub), cex = 0.72 * font_scale, font = 2)
  text(x_pi, y_opi, sprintf("[%.2f, %.2f]", pi_all$pi.lb, pi_all$pi.ub), cex = 0.72 * font_scale, font = 2)
  text(xlim_left, y_ohet, pos = 4, cex = 0.72 * font_scale,
       bquote(paste("Overall heterogeneity: ", I^2, "=", .(sprintf("%.1f%%", m_all$I2)),
                    ", ", tau^2, "=", .(sprintf("%.3f", m_all$tau2)),
                    ", p ", .(fmtp(m_all$QEp)))))

  dom <- c("(A) Bias arising from the randomization process (sequence generation)",
           "(B) Bias due to allocation concealment",
           "(C) Bias due to blinding of participants and personnel",
           "(D) Bias due to blinding of outcome assessment",
           "(E) Bias due to missing outcome data",
           "(F) Bias in selection of the reported result",
           "(G) Bias from other sources")
  mtext("Risk of bias:  + low    ? unclear    \u2212 high",
        side = 1, line = 4.0, adj = 0, cex = 0.68 * font_scale, font = 2)
  for (i in seq_along(dom)) mtext(dom[i], side = 1, line = 4.0 + i * 0.80, adj = 0, cex = 0.6 * font_scale)

  }

  pdf(paste0(filename, ".pdf"), width = width, height = height)
  render(); dev.off()
  tiff(paste0(filename, ".tiff"), width = width, height = height,
       units = "in", res = 300, compression = "lzw")
  render(); dev.off()
}
```

# Primary pooled estimates

```{r}
m_mgadl <- run_primary(d_mgadl, "mgadl_change", "mgadl_vi", "MG-ADL")
m_qmg   <- run_primary(d_qmg,   "qmg_change",   "qmg_vi",   "QMG")
m_mgc   <- run_primary(d_mgc,   "mgc_change",   "mgc_vi",   "MGC")
```

# Forest plots grouped by era (main figures)

```{r}
plot_forest_metafor_grouped(d_mgadl, "mgadl_change", "mgadl_vi", "mgadl_change", "mgadl_change_sd",
  "era_2017", c("pre_2017","2017_plus"), c("Pre-2017","Contemporary (2017+)"),
  "MG-ADL", "forest_mgadl", axis_by = 1)
plot_forest_metafor_grouped(d_qmg, "qmg_change", "qmg_vi", "qmg_change", "qmg_change_sd",
  "era_2017", c("pre_2017","2017_plus"), c("Pre-2017","Contemporary (2017+)"),
  "QMG", "forest_qmg", axis_by = 1)
plot_forest_metafor_grouped(d_mgc, "mgc_change", "mgc_vi", "mgc_change", "mgc_change_sd",
  "era_2017", c("pre_2017","2017_plus"), c("Pre-2017","Contemporary (2017+)"),
  "MGC", "forest_mgc", axis_by = 2)
```

# Subgroup analyses

Subgroups: contemporary vs older trials, stable vs taper steroids.

```{r}
d_mgadl_modern <- filter(d_mgadl, era_2017 == "2017_plus")
d_qmg_modern   <- filter(d_qmg,   era_2017 == "2017_plus")
d_mgc_modern   <- filter(d_mgc,   era_2017 == "2017_plus")

d_mgadl_stable <- filter(d_mgadl, steroid_change == "Stable")
d_qmg_stable   <- filter(d_qmg,   steroid_change == "Stable")
d_mgc_stable   <- filter(d_mgc,   steroid_change == "Stable")

m_mgadl_modern <- run_subgroup(d_mgadl_modern, "mgadl_change", "mgadl_vi", "MG-ADL", "Contemporary (2017+)")
m_qmg_modern   <- run_subgroup(d_qmg_modern,   "qmg_change",   "qmg_vi",   "QMG",    "Contemporary (2017+)")
m_mgc_modern   <- run_subgroup(d_mgc_modern,   "mgc_change",   "mgc_vi",   "MGC",    "Contemporary (2017+)")

m_mgadl_stable <- run_subgroup(d_mgadl_stable, "mgadl_change", "mgadl_vi", "MG-ADL", "Stable steroids")
m_qmg_stable   <- run_subgroup(d_qmg_stable,   "qmg_change",   "qmg_vi",   "QMG",    "Stable steroids")
m_mgc_stable   <- run_subgroup(d_mgc_stable,   "mgc_change",   "mgc_vi",   "MGC",    "Stable steroids")

run_subgroup_test <- function(data, yi_col, vi_col, mod_var, outcome_label, mod_label) {
  d <- data[!is.na(data[[mod_var]]), ]
  d[[mod_var]] <- droplevels(factor(d[[mod_var]]))
  levs <- levels(d[[mod_var]])
  m_test <- rma(yi = d[[yi_col]], vi = d[[vi_col]],
                mods = as.formula(paste0("~ ", mod_var)),
                method = "REML", test = "knha", data = d)
  p_between <- round(m_test$QMp, 4)
  cat(sprintf("[%s | %s] between-group p = %.4f\n", outcome_label, mod_label, m_test$QMp))
  bind_rows(lapply(levs, function(lv) {
    di <- d[d[[mod_var]] == lv, ]
    if (nrow(di) < 3) return(NULL)
    mi <- rma(yi = di[[yi_col]], vi = di[[vi_col]],
              method = "REML", test = "knha", data = di)
    pi <- predict(mi)
    tibble(Outcome = outcome_label, Subgroup = mod_label, Level = lv, k = mi$k,
           Estimate = round(mi$b[1], 3),
           CI_lower = round(mi$ci.lb, 3), CI_upper = round(mi$ci.ub, 3),
           PI_lower = round(pi$pi.lb, 3), PI_upper = round(pi$pi.ub, 3),
           I2_pct = round(mi$I2, 1), tau2 = round(mi$tau2, 4),
           p_between = p_between)
  }))
}

subgroup_specs <- list(
  c(mod = "era_2017",       lab = "Contemporary vs pre-2017"),
  c(mod = "steroid_change", lab = "Stable vs taper steroids")
)

subgroup_results <- bind_rows(lapply(subgroup_specs, function(s) {
  bind_rows(
    run_subgroup_test(d_mgadl, "mgadl_change", "mgadl_vi", s["mod"], "MG-ADL", s["lab"]),
    run_subgroup_test(d_qmg,   "qmg_change",   "qmg_vi",   s["mod"], "QMG",    s["lab"]),
    run_subgroup_test(d_mgc,   "mgc_change",   "mgc_vi",   s["mod"], "MGC",    s["lab"])
  )
}))
print(subgroup_results, row.names = FALSE)
write.csv(subgroup_results, "results_subgroup_summary.csv", row.names = FALSE)
```

## Steroid-subgroup forest plots (supplement)

```{r}
plot_forest_metafor_grouped(d_mgadl, "mgadl_change", "mgadl_vi", "mgadl_change", "mgadl_change_sd",
  "steroid_change", c("Stable","Taper"), c("Stable steroids","Tapered steroids"),
  "MG-ADL", "forest_mgadl_steroid", axis_by = 1)
plot_forest_metafor_grouped(d_qmg, "qmg_change", "qmg_vi", "qmg_change", "qmg_change_sd",
  "steroid_change", c("Stable","Taper"), c("Stable steroids","Tapered steroids"),
  "QMG", "forest_qmg_steroid", axis_by = 1)
plot_forest_metafor_grouped(d_mgc, "mgc_change", "mgc_vi", "mgc_change", "mgc_change_sd",
  "steroid_change", c("Stable","Taper"), c("Stable steroids","Tapered steroids"),
  "MGC", "forest_mgc_steroid", axis_by = 2)
```

# Sensitivity analyses

Restricted fits: phase 3 only, parallel only.

```{r}
d_mgadl_p3 <- filter(d_mgadl, phase == "Phase 3")
d_qmg_p3   <- filter(d_qmg,   phase == "Phase 3")
d_mgc_p3   <- filter(d_mgc,   phase == "Phase 3")

d_mgadl_nx <- filter(d_mgadl, crossover == "Parallel")
d_qmg_nx   <- filter(d_qmg,   crossover == "Parallel")
d_mgc_nx   <- filter(d_mgc,   crossover == "Parallel")

m_mgadl_p3 <- run_subgroup(d_mgadl_p3, "mgadl_change", "mgadl_vi", "MG-ADL", "Phase 3 only")
m_qmg_p3   <- run_subgroup(d_qmg_p3,   "qmg_change",   "qmg_vi",   "QMG",    "Phase 3 only")
m_mgc_p3   <- run_subgroup(d_mgc_p3,   "mgc_change",   "mgc_vi",   "MGC",    "Phase 3 only")

m_mgadl_nx <- run_subgroup(d_mgadl_nx, "mgadl_change", "mgadl_vi", "MG-ADL", "Parallel only")
m_qmg_nx   <- run_subgroup(d_qmg_nx,   "qmg_change",   "qmg_vi",   "QMG",    "Parallel only")
m_mgc_nx   <- run_subgroup(d_mgc_nx,   "mgc_change",   "mgc_vi",   "MGC",    "Parallel only")

sensitivity_results <- bind_rows(
  results_table(m_mgadl_p3, "MG-ADL", "Phase 3 only"),
  results_table(m_qmg_p3,   "QMG",    "Phase 3 only"),
  results_table(m_mgc_p3,   "MGC",    "Phase 3 only"),
  results_table(m_mgadl_nx, "MG-ADL", "Parallel only"),
  results_table(m_qmg_nx,   "QMG",    "Parallel only"),
  results_table(m_mgc_nx,   "MGC",    "Parallel only")
)
print(sensitivity_results, row.names = FALSE)
write.csv(sensitivity_results, "results_sensitivity_summary.csv", row.names = FALSE)
```

## Leave-one-out sensitivity

```{r}
loo_mgadl <- leave1out(m_mgadl, method = "REML")
loo_qmg   <- leave1out(m_qmg,   method = "REML")
loo_mgc   <- leave1out(m_mgc,   method = "REML")

plot_loo <- function(loo_obj, data, label, overall_model, filename, width = 9, height = 9) {
  pdf(filename, width = width, height = height)
  forest(x = loo_obj$estimate, ci.lb = loo_obj$ci.lb, ci.ub = loo_obj$ci.ub,
         slab = data$study_id,
         xlab = paste0("Pooled ", label, " change (leave-one-out)"),
         main = paste0("Leave-one-out sensitivity \u2212 ", label),
         refline = as.numeric(overall_model$b), col = "steelblue", shade = "zebra")
  dev.off()
}

plot_loo(loo_mgadl, d_mgadl, "MG-ADL", m_mgadl, "loo_mgadl.pdf", 9, 9)
plot_loo(loo_qmg,   d_qmg,   "QMG",    m_qmg,   "loo_qmg.pdf",   9, 10)
plot_loo(loo_mgc,   d_mgc,   "MGC",    m_mgc,   "loo_mgc.pdf",   9, 8)
```

# Meta-regression: study-level predictors

Pre-specified moderators (univariable): mean age, female %, MGFA % class III-V,
AChR-seropositive %, route (ref = IV), assessment timepoint (weeks), rescue rate (%).

```{r}
mr_mgadl_age    <- run_metareg(filter(d_mgadl, !is.na(age_mean)),         "mgadl_change","mgadl_vi", ~age_mean,        "MG-ADL","Mean age")
mr_mgadl_sex    <- run_metareg(filter(d_mgadl, !is.na(female_pct)),       "mgadl_change","mgadl_vi", ~female_pct,      "MG-ADL","Female%")
mr_mgadl_mgfa   <- run_metareg(filter(d_mgadl, !is.na(mgfa_severe_pct)),  "mgadl_change","mgadl_vi", ~mgfa_severe_pct, "MG-ADL","MGFA %III-V")
mr_mgadl_achr   <- run_metareg(filter(d_mgadl, !is.na(achr_pct)),         "mgadl_change","mgadl_vi", ~achr_pct,        "MG-ADL","AChR%")
mr_mgadl_route  <- run_metareg(d_mgadl,                                   "mgadl_change","mgadl_vi", ~route,           "MG-ADL","Route (ref=IV)")
mr_mgadl_tp     <- run_metareg(filter(d_mgadl, !is.na(tp_mgadl_wk)),      "mgadl_change","mgadl_vi", ~tp_mgadl_wk,     "MG-ADL","Timepoint (wk)")
mr_mgadl_rescue <- run_metareg(filter(d_mgadl, !is.na(rescue_rate_num)),  "mgadl_change","mgadl_vi", ~rescue_rate_num, "MG-ADL","Rescue rate (%)")

mr_qmg_age    <- run_metareg(filter(d_qmg, !is.na(age_mean)),         "qmg_change","qmg_vi", ~age_mean,        "QMG","Mean age")
mr_qmg_sex    <- run_metareg(filter(d_qmg, !is.na(female_pct)),       "qmg_change","qmg_vi", ~female_pct,      "QMG","Female%")
mr_qmg_mgfa   <- run_metareg(filter(d_qmg, !is.na(mgfa_severe_pct)),  "qmg_change","qmg_vi", ~mgfa_severe_pct, "QMG","MGFA %III-V")
mr_qmg_achr   <- run_metareg(filter(d_qmg, !is.na(achr_pct)),         "qmg_change","qmg_vi", ~achr_pct,        "QMG","AChR%")
mr_qmg_route  <- run_metareg(d_qmg,                                   "qmg_change","qmg_vi", ~route,           "QMG","Route (ref=IV)")
mr_qmg_tp     <- run_metareg(filter(d_qmg, !is.na(tp_qmg_wk)),        "qmg_change","qmg_vi", ~tp_qmg_wk,       "QMG","Timepoint (wk)")
mr_qmg_rescue <- run_metareg(filter(d_qmg, !is.na(rescue_rate_num)),  "qmg_change","qmg_vi", ~rescue_rate_num, "QMG","Rescue rate (%)")

mr_mgc_age    <- run_metareg(filter(d_mgc, !is.na(age_mean)),         "mgc_change","mgc_vi", ~age_mean,        "MGC","Mean age")
mr_mgc_sex    <- run_metareg(filter(d_mgc, !is.na(female_pct)),       "mgc_change","mgc_vi", ~female_pct,      "MGC","Female%")
mr_mgc_mgfa   <- run_metareg(filter(d_mgc, !is.na(mgfa_severe_pct)),  "mgc_change","mgc_vi", ~mgfa_severe_pct, "MGC","MGFA %III-V")
mr_mgc_achr   <- run_metareg(filter(d_mgc, !is.na(achr_pct)),         "mgc_change","mgc_vi", ~achr_pct,        "MGC","AChR%")
mr_mgc_route  <- run_metareg(d_mgc,                                   "mgc_change","mgc_vi", ~route,           "MGC","Route (ref=IV)")
mr_mgc_tp     <- run_metareg(filter(d_mgc, !is.na(tp_mgc_wk)),        "mgc_change","mgc_vi", ~tp_mgc_wk,       "MGC","Timepoint (wk)")
mr_mgc_rescue <- run_metareg(filter(d_mgc, !is.na(rescue_rate_num)),  "mgc_change","mgc_vi", ~rescue_rate_num, "MGC","Rescue rate (%)")
```

# MCID probabilities

```{r}
mcid_prob <- function(model, mcid, outcome_label, subgroup_label) {
  mu <- as.numeric(model$beta); tau2 <- model$tau2; se_mu <- model$se; k <- model$k
  pred_scale <- sqrt(tau2 + se_mu^2); df_pred <- max(k - 2L, 1L)
  p_pred <- pt((-mcid - mu) / pred_scale, df = df_pred)
  p_mean <- pt((-mcid - mu) / se_mu, df = k - 1L)
  tibble(Outcome = outcome_label, Subgroup = subgroup_label, MCID = mcid, k = k,
         mu = round(mu, 3), tau2 = round(tau2, 4), SE_pooled = round(se_mu, 3),
         Pred_scale = round(pred_scale, 3),
         P_future_trial = round(p_pred * 100, 1), P_pooled_mean = round(p_mean * 100, 1))
}

results_mcid <- bind_rows(
  mcid_prob(m_mgadl,        2, "MG-ADL", "All studies"),
  mcid_prob(m_qmg,          2, "QMG",    "All studies (MCID=2)"),
  mcid_prob(m_qmg,          3, "QMG",    "All studies (MCID=3)"),
  mcid_prob(m_mgc,          3, "MGC",    "All studies"),
  mcid_prob(m_mgadl_modern, 2, "MG-ADL", "2017+"),
  mcid_prob(m_qmg_modern,   2, "QMG",    "2017+ (MCID=2)"),
  mcid_prob(m_qmg_modern,   3, "QMG",    "2017+ (MCID=3)"),
  mcid_prob(m_mgc_modern,   3, "MGC",    "2017+"),
  mcid_prob(m_mgadl_stable, 2, "MG-ADL", "Stable steroids only"),
  mcid_prob(m_qmg_stable,   3, "QMG",    "Stable steroids only"),
  mcid_prob(m_mgc_stable,   3, "MGC",    "Stable steroids only")
)
print(results_mcid, row.names = FALSE)
write.csv(results_mcid, "results_mcid.csv", row.names = FALSE)

results_mcid_modern <- bind_rows(
  mcid_prob(m_mgadl_modern, 2, "MG-ADL", "2017+ contemporary"),
  mcid_prob(m_qmg_modern,   2, "QMG",    "2017+ contemporary (MCID=2)"),
  mcid_prob(m_qmg_modern,   3, "QMG",    "2017+ contemporary (MCID=3)"),
  mcid_prob(m_mgc_modern,   3, "MGC",    "2017+ contemporary")
)
write.csv(results_mcid_modern, "results_mcid_contemporary.csv", row.names = FALSE)
```

# Within-trial SD of placebo-arm change (descriptive)

```{r}
within_sd <- bind_rows(
  tibble(Outcome = "MG-ADL", Subset = "All trials",
         k = sum(!is.na(d_mgadl$mgadl_change_sd)),
         Median = round(median(d_mgadl$mgadl_change_sd, na.rm = TRUE), 2),
         IQR_lower = round(quantile(d_mgadl$mgadl_change_sd, 0.25, na.rm = TRUE), 2),
         IQR_upper = round(quantile(d_mgadl$mgadl_change_sd, 0.75, na.rm = TRUE), 2)),
  tibble(Outcome = "QMG", Subset = "All trials",
         k = sum(!is.na(d_qmg$qmg_change_sd)),
         Median = round(median(d_qmg$qmg_change_sd, na.rm = TRUE), 2),
         IQR_lower = round(quantile(d_qmg$qmg_change_sd, 0.25, na.rm = TRUE), 2),
         IQR_upper = round(quantile(d_qmg$qmg_change_sd, 0.75, na.rm = TRUE), 2)),
  tibble(Outcome = "MGC", Subset = "All trials",
         k = sum(!is.na(d_mgc$mgc_change_sd)),
         Median = round(median(d_mgc$mgc_change_sd, na.rm = TRUE), 2),
         IQR_lower = round(quantile(d_mgc$mgc_change_sd, 0.25, na.rm = TRUE), 2),
         IQR_upper = round(quantile(d_mgc$mgc_change_sd, 0.75, na.rm = TRUE), 2)),
  tibble(Outcome = "MG-ADL", Subset = "Contemporary (2017+)",
         k = sum(!is.na(d_mgadl_modern$mgadl_change_sd)),
         Median = round(median(d_mgadl_modern$mgadl_change_sd, na.rm = TRUE), 2),
         IQR_lower = round(quantile(d_mgadl_modern$mgadl_change_sd, 0.25, na.rm = TRUE), 2),
         IQR_upper = round(quantile(d_mgadl_modern$mgadl_change_sd, 0.75, na.rm = TRUE), 2)),
  tibble(Outcome = "QMG", Subset = "Contemporary (2017+)",
         k = sum(!is.na(d_qmg_modern$qmg_change_sd)),
         Median = round(median(d_qmg_modern$qmg_change_sd, na.rm = TRUE), 2),
         IQR_lower = round(quantile(d_qmg_modern$qmg_change_sd, 0.25, na.rm = TRUE), 2),
         IQR_upper = round(quantile(d_qmg_modern$qmg_change_sd, 0.75, na.rm = TRUE), 2)),
  tibble(Outcome = "MGC", Subset = "Contemporary (2017+)",
         k = sum(!is.na(d_mgc_modern$mgc_change_sd)),
         Median = round(median(d_mgc_modern$mgc_change_sd, na.rm = TRUE), 2),
         IQR_lower = round(quantile(d_mgc_modern$mgc_change_sd, 0.25, na.rm = TRUE), 2),
         IQR_upper = round(quantile(d_mgc_modern$mgc_change_sd, 0.75, na.rm = TRUE), 2))
)
print(within_sd, row.names = FALSE)
write.csv(within_sd, "results_within_trial_sd.csv", row.names = FALSE)
```

# Summary tables

```{r}
res_tbl <- bind_rows(
  results_table(m_mgadl, "MG-ADL"),
  results_table(m_qmg,   "QMG"),
  results_table(m_mgc,   "MGC")
)
write.csv(res_tbl, "results_primary_summary.csv", row.names = FALSE)

mr_summary <- bind_rows(
  extract_mr(mr_mgadl_age,    "Mean age",        "MG-ADL", sum(!is.na(d_mgadl$age_mean))),
  extract_mr(mr_mgadl_sex,    "Female%",         "MG-ADL", sum(!is.na(d_mgadl$female_pct))),
  extract_mr(mr_mgadl_mgfa,   "MGFA %III-V",     "MG-ADL", sum(!is.na(d_mgadl$mgfa_severe_pct))),
  extract_mr(mr_mgadl_achr,   "AChR%",           "MG-ADL", sum(!is.na(d_mgadl$achr_pct))),
  extract_mr(mr_mgadl_route,  "Route (ref=IV)",  "MG-ADL", nrow(d_mgadl)),
  extract_mr(mr_mgadl_tp,     "Timepoint (wk)",  "MG-ADL", sum(!is.na(d_mgadl$tp_mgadl_wk))),
  extract_mr(mr_mgadl_rescue, "Rescue rate (%)", "MG-ADL", sum(!is.na(d_mgadl$rescue_rate_num))),
  extract_mr(mr_qmg_age,    "Mean age",        "QMG", sum(!is.na(d_qmg$age_mean))),
  extract_mr(mr_qmg_sex,    "Female%",         "QMG", sum(!is.na(d_qmg$female_pct))),
  extract_mr(mr_qmg_mgfa,   "MGFA %III-V",     "QMG", sum(!is.na(d_qmg$mgfa_severe_pct))),
  extract_mr(mr_qmg_achr,   "AChR%",           "QMG", sum(!is.na(d_qmg$achr_pct))),
  extract_mr(mr_qmg_route,  "Route (ref=IV)",  "QMG", nrow(d_qmg)),
  extract_mr(mr_qmg_tp,     "Timepoint (wk)",  "QMG", sum(!is.na(d_qmg$tp_qmg_wk))),
  extract_mr(mr_qmg_rescue, "Rescue rate (%)", "QMG", sum(!is.na(d_qmg$rescue_rate_num))),
  extract_mr(mr_mgc_age,    "Mean age",        "MGC", sum(!is.na(d_mgc$age_mean))),
  extract_mr(mr_mgc_sex,    "Female%",         "MGC", sum(!is.na(d_mgc$female_pct))),
  extract_mr(mr_mgc_mgfa,   "MGFA %III-V",     "MGC", sum(!is.na(d_mgc$mgfa_severe_pct))),
  extract_mr(mr_mgc_achr,   "AChR%",           "MGC", sum(!is.na(d_mgc$achr_pct))),
  extract_mr(mr_mgc_route,  "Route (ref=IV)",  "MGC", nrow(d_mgc)),
  extract_mr(mr_mgc_tp,     "Timepoint (wk)",  "MGC", sum(!is.na(d_mgc$tp_mgc_wk))),
  extract_mr(mr_mgc_rescue, "Rescue rate (%)", "MGC", sum(!is.na(d_mgc$rescue_rate_num)))
)
write.csv(mr_summary, "results_metaregression.csv", row.names = FALSE)
```
